\section{Introduction}
\label{sec:introduction}

Web accessibility evaluation remains caught between two incomplete modes of practice. On one side, automated tools quickly surface common failures such as missing labels, invalid ARIA, or contrast errors. On the other side, experienced auditors still need to manually inspect interaction patterns, focus behavior, and state-dependent interface changes that are difficult to formalize or automate. W3C guidance explicitly cautions that no single tool can determine whether a site is accessible, and prior work has shown the harm of relying on automated checks alone~\cite{w3cEvalOverview,vigo2013benchmarking}. The continuing prevalence of accessibility failures on popular websites underscores the practical importance of this gap~\cite{webaim2026}.

This gap is widening as web interfaces become more interactive and visually dense. WCAG~2.2 adds requirements that are especially relevant to contemporary web applications, including target size, focus visibility, and input patterns that are often state-dependent~\cite{wcag22rec,wcag22new}. At the same time, visualization research has shown that charts demand richer accessibility support than a basic alt text or table link, because readers need structure, navigation, and description to explore data non-visually~\cite{zong2022rich,blanco2022olli}. Yet the dominant browser-based auditing workflows remain largely page-static and checklist-oriented.

We argue that accessibility auditing for modern web applications should be treated as an inspection problem as much as a detection problem. Auditors need representations that keep geometric evidence, keyboard structure, color usage, and chart metadata close to the live page they are debugging. To support this workflow, we developed \textit{Site Accessibility Auditor}, a Chrome DevTools extension that brings several focused audit views into a single browser-integrated environment.

The paper makes three contributions. First, we present a systems design for \textit{browser-integrated accessibility inspection} inside DevTools, built around complementary panels for touch targets, tab order, charts, and color usage. Second, we introduce a \textit{visualization-aware audit workflow} that treats charts as explicit audit targets rather than generic images, surfacing risks such as missing names, absent summaries, limited keyboard reachability, and likely color-only encodings. Third, we show how \textit{AI-assisted color semantics} can complement deterministic inspection by grouping page colors into meaningful sections and flagging likely accessibility risks without replacing the underlying page evidence. Rather than claiming full automation, our goal is to provide a practical environment that helps developers and researchers inspect accessibility problems that static scans under-represent.
